A Switching Planner for Combined Task and Observation Planning

### 2010-11-28 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
Added plots with results, and a bit more writing on evaluation.

\subsection{Implementation}

The implementation of the continual planning and switching parts is
based on MAPSIM \cite{brenner:nebel:jaamas09} and is able to use several planners as
the underlying planning system. We use a modified version of Fast
Downward \cite{fast-downward}, which we extended with the support for
actions with probabilities.

Our implementation uses the
~\citeauthor{king:2009}~(\citeyear{king:2009}) \system{dlib-ml} for
successive estimation of the underlying belief-state.

@@

\subsection{Experiments}
For evaluation, we used a robot exploration domain similar to the one
used on a physical robotic system. The goal of the robot is to find
objects in a human environment and reporting back their position to a
human.

@@

We conducted experiments on scenarios of several sizes with several
kinds of goals (though the goal is always reporting the position of a
certain kind of object). In order to determine the impact of sensor
reliability on both approaches, we also ran several tests in identical
problems with different probabilities for sensing the goal object.
These problems are denoted by the -easy, -medium and -hard suffixes;
in the easy case the probability of percieving the object is 0.9, in
medium it is 0.65 and 0.4 in hard.

As the initial state of the problems is stochastic, we ran 50
simulations for each configuration. In each run the simulator
generated the true world state by sampling from the same initial state
distribution the planner was using. So on average the world did
conform to the planner's expectations. Not all problems generated in
this manner have a solution. We did not reject these problems, as we
think that detecting the non-existance of a solution is as valuable in
exploration problems than finding one.

@@

The graphs show the average costs of the agent's actions, the number
of solved tasks as a percentage of the solvable tasks, as well as the
planing time for the continual and decision theoretic planners.

For objects that can be easily detected there is little gain in using
a decision theoretic planner, as the greedy sensing appoach by the
baseline continual planner is obviously sufficient here. With
decreasing sensor reliability the more sophisticated observation
planning pays off: while the resulting plans are still longer on
average, the impact on the number of solved tasks was much smaller
than for the baseline system.

We think that a part of the improvement is due to the segmentation of
the plan into several subtask, essentially performing hierarchical
planning. Especially when the continual planner performs badly this is
a huge gain.

>>>>

The implementation of the continual planning and switching parts is
based on MAPSIM \cite{brenner:nebel:jaamas09} and is able to use
several planners as the underlying planning system. We use a modified
version of Fast Downward \cite{fast-downward}, which we extended with
the support for actions with success probabilities. Finally, we use
\system{dlib-ml} \cite{king:2009} for successive estimation of the
underlying belief-state.

@@

To test our approch we use a robot exploration domain similar to the
one used on a physical robotic system. It involves a robot exploring
an office or living environment and trying to return objects to their
owner.

@@

We conducted experiments on scenarios of several sizes with several
kinds of goals (though the goal is always reporting the position of a
certain kind of object). In order to determine the impact of sensor
reliability on both approaches, we also ran several tests in identical
problems with different probabilities for sensing the goal object. The
perception probabilities were 0.9, 9.65 and 04. As the initial state
of the problems is stochastic, we ran 50 simulations for each
configuration. The samples for the true initial state were drawn from
the same distribution that was used for planning, so the planner's
model matched its simulated world exactly. Not all problems generated
in this manner have a solution. We did not reject these problems, as
we believe that detecting the non-existance of a solution is as valuable
in exploration problems than finding one.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{dora1-time}
  \includegraphics{dora2-time}
  \includegraphics{dora3-time}
  \includegraphics{dora4-time}
  \includegraphics{dora56-time}
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{dora1-quality}
  \includegraphics{dora2-quality}
  \includegraphics{dora3-quality}
  \includegraphics{dora4-quality}
  \includegraphics{dora56-quality}
  \caption{Average plan costs and number of successful runs}
  \label{fig:results-quality}
\end{figure}

The graphs in figure \ref{fig:results-time} show the average planning
times. For the smaller belief states, the cost for the decision
theoretic planning is compensated by the decrease of time spent in
Fast Downward.

Figure \ref{fig:results-quality} shows the average costs of the
executed plans as well as the percentage of solvable tasks that were
actually solved by the planner. For objects that can be easily
detected there is little gain in using a decision theoretic planner,
as the greedy sensing appoach by the baseline continual planner is
obviously sufficient here. With decreasing sensor reliability the more
sophisticated observation planning pays off: while the resulting plans
are still longer on average, the impact on the number of solved tasks
was much smaller than for the baseline system.

Impact of state space size: the configuration with a belief space size
of 200 was noticably slower than the other configurations while having
no noticable benefit.

We believe that a part of the improvement is due to the segmentation of
the plan into several subtask, essentially performing hierarchical
planning. Especially when the continual planner performs badly this is
a huge gain.
